\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity}

### 2013-11-26 docs/paper/paper.tex
Initial writings for methods.

\section{Methods}

>>>>

\section{Methods}
The original PC algorithm assumes causal sufficiency, excluding common confounders between nodes.
An adaptation of this algorithm by Spirtes et al. yielded Modified PC, which returns a Markov equivalence class, rather than one specific instance of it.
In literature it is this algorithm that is usually cited.

As mentioned earlier, PC Algorithm has stability problems as the final solution depends on an initial ordering of vertices.
This problem decreases when considering Modified PC; as latent common confounders are not excluded by design bi-directional arrows occur in subgraphs where original PC would attempt to direct a single arrow in either direction depending on node ordering.

In a more recent publication by Ramsey et al. \cite{ramsey2012} a weaker but still sufficient assumption for graph faithfulness in PC algorithm is introduced.
The resulting algorithmic changes provide better results and is able to mark unshielded triples as unfaithful.
However, this method also require a significant amount of additional conditional independence tests.

Based on similar ideas, we answer whether an unshielded triple is faithful based on already done conditional independence tests.
